---
title: "data602 assignment4"
author: "jim lung"
date: "11-09-2017"
output: html_document
---

# data602 assignment4

Deliverable: A url to a private repository on Github with the R script

Note: Docker image is not required for assignment #4

Take at least two of the time-series analytics performed in assignment #2 (listed below) and redo it in R. The time-series you can choose from are

5 day moving average
20 day moving average
5 day moving standard deviation
20 day moving standard deviation
Bollinger bands 2 standard deviation
Daily returns %
Daily return mean %
Price range for the day (bars)
Daily price difference
Distribution of prices (Gaussian distribution, aka bell curve)

Load the data that is sitting on a publicly available site via a URL  (i.e. Dropbox, S3, public Github - only the data can be public), the data does not need to be in a database and can be static. The larger the dataset the better. Feel free to add your own time-series in addition to choosing 2 from above.

For this assignment, a Docker image is not required, only a link to a private Github repo containing the R script that can be executed and produces results without any setup



## Scraping and analysis:

```{r}
library(rvest)
library(RCurl)
library(XML)
```

## Create function for scraping data from web
```{r}

ddd <- function(i){


hkurl <- i

'ratings' <- function(hkurl)
  {
  require(XML)

hdoc <- getURLContent(hkurl)

# find all tables in webpage
hktables <- readHTMLTable(hdoc)

# find largest table and return as dataframe
columns <- unlist(lapply(hktables, function(t) dim(t)[2]))
 
df <- hktables[[max(columns)]]
 
return(df)
}

seriess <- ratings(hkurl)
colnames(seriess) <- c("Date","Open","High","Low","Close","Volume")
seriess
return(seriess)
}


```

## Create Dataframe by using function
```{r}
# Real time data for aapl
aapl3 <- ddd('http://www.nasdaq.com/symbol/aapl/historical')
head(aapl3)

# Real time data for amzn
amzn3 <- ddd('http://www.nasdaq.com/symbol/amzn/historical')
head(amzn3)

# Real time data for intc
intc3 <- ddd('http://www.nasdaq.com/symbol/intc/historical')
head(intc3)

# Real time data for msft
msft3 <- ddd('http://www.nasdaq.com/symbol/msft/historical')
head(msft3)

# Real time data for snap
snap3 <- ddd('http://www.nasdaq.com/symbol/snap/historical')
head(snap3)

```

## Replace text of today and remove comma
```{r}
# Get the text of today
library(lubridate)
date <- today()
newdate <- strptime(as.character(date), "%Y-%m-%d")
txtdate <- format(newdate, "%m/%d/%Y")
txtdate

# remove comma fuction
removeComma= function(s) {gsub(",", "", s, fixed = TRUE)}
```

## Function of calcuation of analysis
```{r}
abc <- function(z){
#colnames(z) <- c("Date","Open","High","Low","Close","Volume")
z$Date <- as.character(z$Date)
z$Open <- round(as.numeric(as.character(z$Open)),2)
z$High <- round(as.numeric(as.character(z$High)),2)
z$Low <- round(as.numeric(as.character(z$Low)),2)
z$Close <- round(as.numeric(as.character(z$Close)),2)
z$Volume <- as.numeric(as.character(removeComma(z$Volume)))
z[1,1] <- txtdate

z$change <- z$Close - z$Open
z$rating_change <- z$change / z$Open
z$date_range <- z$High - z$Low
z
}


aapl3 <- abc(aapl3)
head(aapl3) 
amzn3 <- abc(amzn3)
head(amzn3)
intc3 <- abc(intc3)
head(intc3)
msft3 <- abc(msft3)
head(msft3)
snap3 <- abc(snap3)
head(snap3)
```

## Cleaning and Analysis 1 - Index comparsion
```{r}
library(tidyr)
library(dplyr)
aapl4 <- aapl3 %>% select(Date, Close)
colnames(aapl4) <- c("Date","AAPL")
amzn4 <- amzn3 %>% select(Date, Close)
colnames(amzn4) <- c("Date","AMZN")
intc4 <- intc3 %>% select(Date, Close)
colnames(intc4) <- c("Date","INTC")
msft4 <- msft3 %>% select(Date, Close)
colnames(msft4) <- c("Date","MSFT")
snap4 <- snap3 %>% select(Date, Close)
colnames(snap4) <- c("Date","SNAP")

# Group and visualization
x <- inner_join(aapl4,amzn4)
y <- inner_join(x,intc4)
z <- inner_join(y,msft4)
analysis1 <- inner_join(z,snap4) 
analysis2 <- analysis1 %>% gather(company, index, 2:6)
head(analysis1)
head(analysis2)

```

## Stock index comparsion

```{r}
library(ggplot2)

graph1 <- ggplot(data=analysis2,
          aes(x=Date, y=index, group=company)) +
          geom_point(size=3, aes(shape=company, color=company)) +
          geom_line(size=1, aes(color=company)) +
          ggtitle("Profiles for stock index comparsion")
graph1
```

# 5 day Moving Average
```{r}
# function for moving average
ma <- function(arr, n){
  res = arr
  for(i in n:length(arr)){
    res[i] = mean(arr[(i-n+1):i])
  }
  res
}

# Using close price to compare
aapl5 <- aapl3 %>% select(Date, Close)
colnames(aapl5) <- c("Date","AAPL")
amzn5 <- amzn3 %>% select(Date, Close)
colnames(amzn5) <- c("Date","AMZN")
intc5 <- intc3 %>% select(Date, Close)
colnames(intc5) <- c("Date","INTC")
msft5 <- msft3 %>% select(Date, Close)
colnames(msft5) <- c("Date","MSFT")
snap5 <- snap3 %>% select(Date, Close)
colnames(snap5) <- c("Date","SNAP")

# Calculate 5 days Moving Average
aapl5$AAPL_SMA <- ma(aapl5$AAPL, 5)
aapl6 <- aapl5 %>% select(Date, AAPL_SMA)

amzn5$AMZN_SMA <- ma(amzn5$AMZN, 5)
amzn6 <- amzn5 %>% select(Date, AMZN_SMA)

intc5$INTC_SMA <- ma(intc5$INTC, 5)
intc6 <- intc5 %>% select(Date, INTC_SMA)

msft5$MSFT_SMA <- ma(msft5$MSFT, 5)
msft6 <- msft5 %>% select(Date, MSFT_SMA)

snap5$SNAP_SMA <- ma(snap5$SNAP, 5)
snap6 <- snap5 %>% select(Date, SNAP_SMA)


# Group and visualization
x <- inner_join(aapl6,amzn6)
y <- inner_join(x,intc6)
z <- inner_join(y,msft6)
analysis3 <- inner_join(z,snap6) 
analysis4 <- analysis3 %>% gather(company, index, 2:6)
head(analysis3)
head(analysis4)

# 5 days Moving average comparison
graph2 <- ggplot(data=analysis4,
          aes(x=Date, y=index, group=company)) +
          geom_point(size=3, aes(shape=company, color=company)) +
          geom_line(size=1, aes(color=company)) +
          ggtitle("5 days Moving average comparison")
graph2
```

# 20 days Moving Average
```{r}
# Using close price to compare
aapl7 <- aapl3 %>% select(Date, Close)
colnames(aapl7) <- c("Date","AAPL")
amzn7 <- amzn3 %>% select(Date, Close)
colnames(amzn7) <- c("Date","AMZN")
intc7 <- intc3 %>% select(Date, Close)
colnames(intc7) <- c("Date","INTC")
msft7 <- msft3 %>% select(Date, Close)
colnames(msft7) <- c("Date","MSFT")
snap7 <- snap3 %>% select(Date, Close)
colnames(snap7) <- c("Date","SNAP")

# Calculate 20 days Moving Average
aapl7$AAPL_SMA <- ma(aapl7$AAPL, 20)
aapl8 <- aapl7 %>% select(Date, AAPL_SMA)

amzn7$AMZN_SMA <- ma(amzn7$AMZN, 20)
amzn8 <- amzn7 %>% select(Date, AMZN_SMA)

intc7$INTC_SMA <- ma(intc7$INTC, 20)
intc8 <- intc7 %>% select(Date, INTC_SMA)

msft7$MSFT_SMA <- ma(msft7$MSFT, 20)
msft8 <- msft7 %>% select(Date, MSFT_SMA)

snap7$SNAP_SMA <- ma(snap7$SNAP, 20)
snap8 <- snap7 %>% select(Date, SNAP_SMA)


# Group and visualization
x <- inner_join(aapl8,amzn8)
y <- inner_join(x,intc8)
z <- inner_join(y,msft8)
analysis5 <- inner_join(z,snap8) 
analysis6 <- analysis5 %>% gather(company, index, 2:6)
head(analysis5)
head(analysis6)

# 20 days Moving average comparison
graph2 <- ggplot(data=analysis6,
          aes(x=Date, y=index, group=company)) +
          geom_point(size=3, aes(shape=company, color=company)) +
          geom_line(size=1, aes(color=company)) +
          ggtitle("20 days Moving average comparison")
graph2

```

# visualization for 3 months
```{r}
library(ggplot2)

aapl9 <- subset(aapl8, Date < "12-01-2017" & Date > "08-22-2017")
x <- ggplot(data = aapl9,  aes(x=Date, y=AAPL_SMA)) + geom_line(col="blue") + geom_point(col="blue", pch=1)
x
amzn9 <- subset(amzn8, Date < "12-01-2017" & Date > "08-22-2017")
x <- ggplot(data = amzn9,  aes(x=Date, y=AMZN_SMA)) + geom_line(col="blue") + geom_point(col="blue", pch=1)
x
intc9 <- subset(intc8, Date < "12-01-2017" & Date > "08-22-2017")
x <- ggplot(data = intc9,  aes(x=Date, y=INTC_SMA)) + geom_line(col="blue") + geom_point(col="blue", pch=1)
x
msft9 <- subset(msft8, Date < "12-01-2017" & Date > "08-22-2017")
x <- ggplot(data = msft9,  aes(x=Date, y=MSFT_SMA)) + geom_line(col="blue") + geom_point(col="blue", pch=1)
x
snap9 <- subset(snap8, Date < "12-01-2017" & Date > "08-22-2017")
x <- ggplot(data = snap9,  aes(x=Date, y=SNAP_SMA)) + geom_line(col="blue") + geom_point(col="blue", pch=1)
x
```


# Market Price
```{r}
library(rvest)
library(XML)

sym <- function(i){
url <- paste('http://www.nasdaq.com/symbol/',i,'/',sep="")
html <- read_html(url)
body_text <- html %>%
        html_nodes("#qwidget_lastsale") %>% 
        html_text()

body_text <- as.numeric(sub('\\$','',body_text))
print(body_text)
}

# use "amzn" as example to run program
sym('amzn')

```

# Create new trade file into CSV
```{r}
# create new dataframe
trade <-data.frame("Side"=character(), "Ticker"=character(), "Quantity"=integer(0), "Price"=integer(0), "Date"=character(),stringsAsFactors = FALSE)



# save dataframe as csv file
write.table(trade, file = "trade.csv", sep = ",", col.names = NA, qmethod = "double")
read.table("trade.csv", header = TRUE, sep = ",") 
```
# Add sell or buy record into CSV file
```{r}
library(dplyr)
#import csv 
x <- read.csv("trade.csv", header = TRUE, sep = ",") 

############### in case to ask for buy or sell, and check the balance


#side <- readline(prompt="Buy or Sell: ")
#ticker <- readline(prompt="ticker: ")
#quantity <- readline(prompt="quantity: ")

# convert character into integer
#quantity <- as.integer(quantity)

#print(paste("You", side,quantity,"stock of", ticker, "."))

#marketvalue = sym(ticker)
#buyvalue = marketvalue * quantity

#if (side == 'buy'){
#  if (cashbal < buyvalue){
#    print("No cash to buy!")
#  } else {
#    x[nrow(x) +1,] <- c(nrow(x)+1, side , ticker , quantity, marketvalue, Sys.Date())
#  }
#}

###########

# add new transaction(example buy and sell, amzn, 30, 1000.46)
x[nrow(x) +1,] <- c(nrow(x)+1,'buy', 'amzn', 30, 1000.46, txtdate)
x[nrow(x) +1,] <- c(nrow(x)+1,'sell', 'amzn', 15, 1100.00, txtdate)

# tidy dataframe
trade = select(x, -1)


# re-write and save over the previous data
write.table(trade, file = "trade.csv", sep = ",", col.names = NA, qmethod = "double")
read.table("trade.csv", header = TRUE, sep = ",") 

```


# Balance of stock
```{r}
# check position
blotter <- read.csv("trade.csv", header = TRUE, sep = ",") 
w =nrow(blotter)
w

# Postition
q <- unique(blotter$Ticker)

b=0
d=0
e=0
f=0
balance <-data.frame("Ticker"=character(), "Quantity"=integer(0), "Price"=integer(0),stringsAsFactors = FALSE)


for (j in q){
for (i in 1:w){
if(blotter$Side[i] == 'buy' & blotter$Ticker[i] == j){
  a = sum(blotter$Quantity[i])
  b = b + a
  e = e + blotter$Price[i]*blotter$Quantity[i]
  }
if(blotter$Side[i] == 'sell' & blotter$Ticker[i] == j){
  c = sum(blotter$Quantity[i])
  d = d + c
  f = f + blotter$Price[i]*blotter$Quantity[i]
}
  bal = b-d
  avg = e/a
  print(bal)

}
balance <- rbind(balance, data.frame("Ticker"=q, "Quantity"=bal, "Price"=avg))
balance <- na.omit(balance)
}
balance

```

# P/L
```{r}
#z
pl <-data.frame("Ticker"=character(), "Position"=integer(0), "Market"=integer(0), "WAP"=integer(0), "UPL"=integer(0), "RPL"=integer(0),stringsAsFactors = FALSE)

# Ticker and Market price
h = nrow(balance)

k <- unique(balance$Ticker)
upl = 0
rpl = 0

for (i in h){
  l = balance$Ticker[i]
  m = balance$Quantity[i]
  n = balance$Price[i]
  y <- as.vector(l)
  o = sym(y)
  marketp = o
  if (marketp > n){
    upl = (marketp-n)*m
    rpl = 0
    upl
  }else{
    rpl = (n-marketp)*m
    upl = 0
    rpl
  }
  #total = upl + rpl
  #share = m/sum(pl$Position)
  #dollar = marketp/sum(pl$Market)
}
pl <- rbind(pl, data.frame("Ticker"=k, "Position"=m, "Market"=o, "WAP"=n, "UPL"=upl, "RPL"=rpl))

total = upl + rpl
share = m/sum(pl$Position)
dollar = marketp/sum(pl$Market)

pl$Total = total
pl$Allocationshare = share
pl$Allocationmarket = dollar
pl

# WAP

```


# check cashbalance
```{r}
blotter <- read.csv("trade.csv", header = TRUE, sep = ",") 

w =nrow(blotter)

z = 100000
p = 0
q = 0
for(i in 1:w){
  if (blotter$Side[i] == 'buy'){
    p = p + blotter$Price[i]*blotter$Quantity[i]
  }
  if (blotter$Side[i] == 'sell'){
    q = q + blotter$Price[i]*blotter$Quantity[i]
  }
}
cashbal = z-p+q
cashbal
```
